\systemnamenospace: Head Orientation Based Selection\\in Physical Spaces

### 2014-08-08 doc/sui14/iteration3.tex
Added distance constraint for iteration3

This absolute orientation cannot be applied to all indoor environments, since
the user's movements through the space could change the relationships between
targets. However, with the constraint that the targets are spread around the
periphery, their relative orientations are stable (see
Figure~\ref{fig:third_principle}).

>>>>

This absolute orientation cannot be applied to all indoor environments, since
the user's movements through the space could change the relationships between
targets. However, with the constraint that the targets are spread around the
periphery at similar distances, their relative orientations are stable (see
Figure~\ref{fig:third_principle}).
